Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-07 paper/paper.tex
revising comments from igor

\begin{itemize}
  \item \textbf{Undefined Behavior.} False positives of this kind are
    manifested when tests cover implementation-dependent behavior, as
    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
    example, one of the tests from \jerry\ uses the function
    \CodeIn{Number.toPrecision([precision])}, which translates a
    number to a string, considering a given number of significant
    digits. The floating-point approximation of the real value is
    implementation-dependent, making the test to pass only in
    \chakra\ for that test. \Igor{ Several tests explores 
    the error message from a function violation, due the error
    message string is distinct and the type of Error is equal,
    we considered these cases as undefined behavior too.
    }

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest when the target
    engine that runs the test do not optimize code as the original
    engine. For that, tests fail to finish at the time budget or runs
    out of memory.\Comment{For example, we found that only \jsc{} implements
    tail-call optimization to avoid tail recursion.}
    \Igor{
      For example, a testcase from \jsc{} suite explores the tail call
      to optimize the recursion, the test uses a recursive function that
      should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
      only the \jsc{} supports tail-call optimization and the testcase 
      passes without failures. Another case can be found in JerryScript suite
      that uses a repetition statement to concatenate long strings 
      exponentially, causing an out of memory error. The engines used 
      supports the flags to increase memory, however we prefer to use 
      the default engine build.
    }

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, Chakra does not
    implement various properties from the \mcodeid{Symbol} object, 
    \Igor{these implementation are in experimental mode 
    (ie. activating with flag -ES6Experimental)}.

  \item \textbf{Unknown.} This source corresponds to the cases we were
    unable to confidently diagnose the failure.
    \Igor{
      We observed that some tests are not valid due
      not corresponds to the ES6 specifications,
      we skip these warnings.
    }

>>>>

\begin{itemize}
  \item \textbf{Undefined Behavior.} False positives of this kind are
    manifested when tests cover implementation-dependent behavior, as
    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
    example, one of the tests from \jerry\ uses the function
    \CodeIn{Number.toPrecision([precision])}, which translates a
    number to a string, considering a given number of significant
    digits. The floating-point approximation of the real value is
    implementation-dependent, making the test to pass only in
    \chakra\ for that test. As another example, some tests from
    \Fix{Y} use the implementation-dependent description message\Mar{what is the
      name of the property?} encapsulated in an \CodeIn{Error} object
    in assertions. As such, those tests fail in all engines but \Fix{Y}.

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest because the
    engine that runs the test does not optimize the code as the
    original engine and that has an effect in the test outcome.  The
    test may fail to finish at the time budget or runs out of
    memory. For example, a test case from \jsc{} defines a function
    with a tail-call recursion. The test fails in all engines but
    \jsc{}, which implements tail-call optimization.

    %% \Igor{
    %%   For example, a testcase from \jsc{} suite explores the tail call
    %%   to optimize the recursion, the test uses a recursive function that
    %%   should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
    %%   only the \jsc{} supports tail-call optimization and the testcase 
    %%   passes without failures. Another case can be found in JerryScript suite
    %%   that uses a repetition statement to concatenate long strings 
    %%   exponentially, causing an out of memory error. The engines used 
    %%   supports the flags to increase memory, however we prefer to use 
    %%   the default engine build.
    %% }

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, Chakra does not
    implement by default various properties from the \mcodeid{Symbol}
    object. These properties are only available activating ES6
    experimental mode with the flag \CodeIn{-ES6Experimental}.

  \item \textbf{Unknown.} This category corresponds to the cases we
    were unable to confidently diagnose the failure.  \Igor{ We
      observed that some tests are not valid due not corresponds to
      the ES6 specifications, we skip these warnings.  }\Mar{Igor,
      this is not well-formed english and I don't understand what you
      want to say.}
